A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-15 paper/ms.tex
update ms (binary companion appendix)
Co-authored-by: adamkraus <alk@astro.as.utexas.edu>

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.7\textwidth]{f15supp.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf Binarity indicators for rotators in \cn.} 
    Data are as in the lower panel of
    Figure~\ref{fig:age}.  Astrometric binaries ($\mathrm{RUWE}>1.2$)
    appear in red; photometric binaries ($>$0.3\,mag above an
    empirical isochrone; 20\% of stars) are orange.  
    Over $0.6<\bpmrpo<1.5$, the detected rotation periods in binaries tend to 
    fall below the slow sequence.
    %FIXME!
		% Over $0.5<\bpmrpo<1.3$, Set $\mathcal{B}$ has \replaced{281}{523} stars.
		% Dividing these stars into ``slow'' and ``fast'' sequences by eye,
		% the fraction of stars showing signs of binarity in the slow and fast
		% subsamples are \replaced{30\% (63/210)}{27\% (106/289)} and
		% \replaced{56\% (40/71)}{51\% (68/134)}, respectively.
		\label{fig:binarity}
	}
\end{figure}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f17.pdf}
			\includegraphics[width=0.48\textwidth]{f6.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler 1627 is a binary.} {\it Left:} High-resolution imaging
    from Gemini-North/`Alopeke and Keck/NIRC2 shows an $\approx$M2V
    companion at $\rho \approx 0\farcs16$, which corresponds to a
    projected separation of $53\pm4$\,AU.  The inset shows a cutout of
    the NIRC2 image (North is up, East is left, scale is set by the
    separation of the binary).  The lines show 5-$\sigma$ contrast
    limits for the `Alopeke filters, and 6-$\sigma$ contrast limits
    for NIRC2.  {\it Left:} Gaia EDR3 renormalized
    unit weight error (RUWE) point estimates for Kepler\,1627A and
    other members of the $\delta$\,Lyr cluster reported by
    \citet{KounkelCovey2019}.  Since other members of the cluster with
    similar brightnesses have comparable degrees of photometric
    variability, the high RUWE suggests that Kepler\,1627 is an
    astrometric binary. 
    \label{fig:kep1627binary}
	}
\end{figure*}

@@

Figure~\ref{fig:kep1627binary} summarizes the results of the
high-resolution imaging.  
The Gaia EDR3 parallax for the primary implies a projected separation
of $53 \pm 4$\,AU, assuming the companion is bound. 
Although the companion is unresolved in the
Gaia source catalog (there are no candidates brighter than $G < 20.5$ mag within $\rho < 120\arcsec$), its existence was also suggested by the primary
star's large RUWE, relative to other members of the \cn.  Given the
large observed RUWE of the primary, and the low geometric probability
that a companion imaged at $\rho \approx 0\farcs16$ is a chance
line-of-sight companion, we proceed under the assumption that the
companion is bound, and that Kepler\,1627 is a binary. 
Given the distance and age, the models of \citet{baraffe_new_2015} imply
a companion mass of $M_{\rm B} \approx 0.33 M_{\odot}$ and companion
temperature of $T_{\rm eff,B} \approx 3450$ K.
The corresponding spectral type is roughly M2.5V \citep{pecaut_mamajek_2013}.
% \footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}, version \texttt{2021/03/02}.}

>>>>

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.7\textwidth]{f15supp.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf Binarity indicators for rotators in \cn.} 
    Data are as in the lower panel of Figure~\ref{fig:age}.  Sources
    with $\mathrm{RUWE}>1.2$ appear in red; these include astrometric binaries as well
    as sources poorly fit by a single-star PSF.  Photometric binaries
    ($>$0.3\,mag above an empirical isochrone; 20\% of stars) are
    orange.  Over $0.6<\bpmrpo<1.5$, the detected rotation periods in
    binaries tend to fall below the slow sequence.
		\label{fig:binarity}
	}
\end{figure}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f17.pdf}
			\includegraphics[width=0.48\textwidth]{f6.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Kepler 1627 is a binary.} {\it Left:} High-resolution imaging
    from Gemini-North/`Alopeke and Keck/NIRC2 shows an $\approx$M2V
    companion at $\rho \approx 0\farcs16$, which corresponds to a
    projected separation of $53\pm4$\,AU.  The inset shows a cutout of
    the NIRC2 image (North is up, East is left, scale is set by the
    separation of the binary).  The lines show 5-$\sigma$ contrast
    limits for the `Alopeke filters, and 6-$\sigma$ contrast limits
    for NIRC2.  {\it Left:} Gaia EDR3 renormalized
    unit weight error (RUWE) point estimates for Kepler\,1627A and
    other members of the $\delta$\,Lyr cluster reported by
    \citet{KounkelCovey2019}.  Since other members of the cluster with
    similar brightnesses have comparable degrees of photometric
    variability, the high RUWE suggests that Kepler\,1627 is a
    binary. 
    \label{fig:kep1627binary}
	}
\end{figure*}

@@

Figure~\ref{fig:kep1627binary} summarizes the results of the
high-resolution imaging.  The Gaia EDR3 parallax for the primary
implies a projected separation of $53 \pm 4$\,AU, assuming the
companion is bound.  Although the companion is unresolved in the Gaia
source catalog (there are no candidates brighter than $G < 20.5$ mag
within $\rho < 120\arcsec$), its existence was also suggested by the
primary star's large RUWE, relative to other members of the \cn.
Based on the apparent separation, the binary orbital period is of
order hundreds of years.  The large RUWE is therefore more likely to
be caused by a PSF-mismatch skewing the Gaia centroiding during
successive scans, rather than true astrometric motion.  Regardless,
given the large observed RUWE of the primary, and the low geometric
probability that a companion imaged at $\rho \approx 0\farcs16$ is a
chance line-of-sight companion, we proceed under the assumption that
the companion is bound, and that Kepler\,1627 is a binary.  Given the
distance and age, the models of \citet{baraffe_new_2015} imply a
companion mass of $M_{\rm B} \approx 0.33 M_{\odot}$ and companion
temperature of $T_{\rm eff,B} \approx 3450$ K.  The corresponding
spectral type is roughly M2.5V \citep{pecaut_mamajek_2013}.
% \footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt}, version \texttt{2021/03/02}.}
